Minimal trap spaces of Logical models are maximal siphons of their Petri net encoding

### 2022-05-13 cmsb22.tex
Remove comments
Update the order authors ...

\title{Minimal trap spaces of Logical models are maximal siphons of their Petri net encoding}
\titlerunning{Minimal trap spaces as maximal siphons}
% \title{Scaling-up attractor computation for Boolean models}
% \vangiang{I like the first title :). Since we only conduct experiments on real-world Boolean models of not too large size, it seems to make less sense to use "scaling-up" (this should be for the journal version).}

\author{Van-Giang Trinh\inst{1}\orcidID{0000-0001-6581-998X} \and \\
  Belaid Benhamou\inst{1} \and \\
  Sylvain Soliman\inst{2}\orcidID{0000-0001-5525-7418} \and \\
  Kunihiko Hiraishi\inst{3}\orcidID{0000-0003-1750-1891}
  }

@@

\institute{%
  LIS, Aix-Marseille Université, Marseille, France\\
  \email{\{trinh.van-giang, belaid.benhamou\}@lis-lab.fr}
  \and
  Lifeware team, Inria Saclay center, Palaiseau, France\\
  \email{Sylvain.Soliman@inria.fr}
  \and
  School of Information Science, Japan Advanced Institute of Science and Technology, Japan\\
  \email{hira@jaist.ac.jp}
}

@@

% \sylvain{This section might be better with real ``Definitions'', but when I tried rewriting it, this led to a lot of changes\dots I guess we can do that for the journal version but for now keep things as they are.}
% \vangiang{Yes. This should be better. We can do that for the journal version.}

@@

% The main property of this encoding is that it is completely faithful w.r.t.\ the asynchronous semantics.
% Asynchronous transitions of the original model correspond one-to-one with firings of transitions in the Petri net.

@@

\begin{theorem}%
\label{theo:min_ts_2_max_sp}
  %\(S\) is a minimal trap space of Boolean model \(\mathcal{M}\) if and only if the places corresponding to the fixed values in \(S\) (active or inactive) are a maximal conflict-free siphon of \((P, T, W)\), the Petri net encoding of \(S\).

@@

% For illustration, we consider the Petri net encoding \(\mathcal{P}\) shown in Figure~\ref{fig:PN}.
% If \(p_{x_1}\) is in a siphon \(S\), then \(\overline{p_{x_1}}\) or \(\overline{p_{x_2}}\) should be in \(S\).
% This rule is translated into the ASP rule
% \[
% \verb|p(x_1, 0) ; p(x_2, 0) :- p(x_1, 1).|
% \] To forbid that \(S\) contains both \(p_{x_1}\) and \(\overline{p_{x_1}}\), we have the ASP rule
% \[
% \verb|:- p(x_1, 1) , p(x_2, 0).|
% \] Analogously for other places in \(\mathcal{P}\), we obtain the final ASP as follows:

>>>>

\title{Minimal trap spaces of Logical models are maximal siphons of their Petri net encoding}
\titlerunning{Minimal trap spaces as maximal siphons}

\author{Van-Giang Trinh\inst{1}\orcidID{0000-0001-6581-998X} \and \\
  Belaid Benhamou\inst{1} \and \\
  Kunihiko Hiraishi\inst{2}\orcidID{0000-0003-1750-1891} \and \\
  Sylvain Soliman\inst{3}\orcidID{0000-0001-5525-7418}
  }

@@

\institute{%
  LIS, Aix-Marseille Université, Marseille, France\\
  \email{\{trinh.van-giang, belaid.benhamou\}@lis-lab.fr}
  \and
  School of Information Science, Japan Advanced Institute of Science and Technology, Japan\\
  \email{hira@jaist.ac.jp}
  \and
  Lifeware team, Inria Saclay center, Palaiseau, France\\
  \email{Sylvain.Soliman@inria.fr}  
}

@@

@@

@@

\begin{theorem}%
\label{theo:min_ts_2_max_sp}

@@
